% Chapter Template

\chapter{Chapter Title Here} % Main chapter title

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

The focus of the report is to show what experiences you made during the project.\\
In other words, what did you learn. It should be a critical eye on both your process and your code.\\
Lessons learned. Why things happened is more interesting than just what happened. \\

This is just an example, feel free to deviate from this setup. \\

%----------------------------------------------------------------------------------------
%	SECTION 0
%----------------------------------------------------------------------------------------

\section{Assignment Text}

Briefly introduce the task

PRESENTATION OF THE GROUP AND WORKING FORM\\
\begin{itemize}
    \item Who has participated
    \item Any roles that have been assigned
    \item How did the group choose to organize the work
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Construction}

Briefly introduce the task, and how you went about constructing solution

Each of these as individual subsections, as you see fit\\
\begin{itemize}
    \item Brief explanation of how the task was solved
    \item Technical choices
    \item High-level explanation of the application
    \item Necessary documentation to understand and to be able to run the code
    \item Explanation of any details necessary to understand the system
\end{itemize}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. 

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. 

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Result}

Introduce your result

Each of these as individual subsections, as you see fit\\
\begin{itemize}
    \item What has the group and/or individuals achieved.
    \item Explain results, show them, figures, examples etc.
\end{itemize}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. 

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Discussion}

Discuss results, construction everything...\\

Each of these as individual subsections, as you see fit\\
\begin{itemize}
    \item What experiences have the group or people made during the project
    \item What worked well?
    \item What didn't work?
    \item Discuss why things have worked or not
    \item Possible alternative solutions (which were not selected)
    \item Suggestions for improvement that could have been implemented along the way and future.improvements to the process or application. 
\end{itemize}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. 

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. 